Constructing Sailing Match Race Schedules: Round-Robin Pairing Lists

### 2015-04-14 paper.tex
some minor typos and rephrases from my PoV

\begin{abstract}
We present a constraint programming solution to the problem of generating round-robin schedules for
dinghy sailing match races. Our schedules satisfy the widely used ISAF World Sailing pairing lists
match race criteria. We show that some published ISAF schedules are in fact illegal, and present
corresponding legal instances and schedules that have not previously been published. Our schedules
can be downloaded as blanks, then populated with actual competitors and used in ISAF competitions.
\end{abstract}

@@

The paper is organised as follows: we introduce the 13 match racing rules, then explain the
constraint models and four stages of schedule construction, and then schedules are presented. We
finish with discussion and a conclusion.

@@

There are some conflicts inherent in the rules. Take criteria~4 and~11, assume we have 4 boats, and
in flight $i$ the last match is the pair of skippers ($x,y$). Criterion~11 dictates that skippers $x$
and $y$ must appear in the next flight, $i+1$, and criterion~4 that neither can be first in the next
flight. This forces skippers $x$ and $y$ to compete in flight $i+1$ as the last match, violating
criterion~1. Therefore, although not explicitly stated, it is not possible to satisfy every criteria
with fewer than 6 boats.

@@

        \begin{scope}[yshift=9.9cm, xshift=-3.5cm]
            \node [anchor=north west] (ModMatchTable) at (0, 0) {
                \begin{minipage}{4.5cm}
                    \centering
                    \setlength{\tabcolsep}{2pt}
                    \setlength{\aboverulesep}{0pt}
                    \setlength{\belowrulesep}{0pt}
                    \setlength{\extrarowheight}{.75ex}
                    \begin{tabular}{cccccccc}
                        & 0 & 1 & 2 & 3 & 4 & 5 & 6 \\ \cmidrule{2-8}
                        \multicolumn{1}{l@{\hspace{1em}}|}{0} & ~-~ & 0 & 1 & 3 & 5 & 2 & 6 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{1} & 0 & ~-~ & 6 & 2 & 3 & 1 & 4 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{2} & 1 & 6 & ~-~ & 0 & 4 & 5 & 2 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{3} & 3 & 2 & 0 & ~-~ & 6 & 4 & 5 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{4} & 5 & 3 & 4 & 6 & ~-~ & 0 & 1 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{5} & 2 & 1 & 5 & 4 & 0 & ~-~ & 3 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{6} & 6 & 4 & 2 & 5 & 1 & 3 & ~-~ \\
                    \end{tabular}
                \end{minipage}
            };
            \node [above=-0.1 of ModMatchTable.north west, anchor=south west] (ModMatch) { $\modMatch$ };
        \end{scope}

@@

We present four pairs of schedules. The first pair is for 8 skippers and 6 boats, one published by
ISAF, the other generated by us. Next, we present two new schedules, not appearing in the ISAF
manual, for 9 skippers and 6 boats and 9 skippers with 8 boats, then 10 skippers and 6 boats, again
ISAF published and generated by us. Finally, we show what is a relatively easy problem, 8 skippers
and 8 boats.  For each of our schedules (with the exception of the "easy-8" problem), we used 1 day
CPU time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance.
Stages 3 and 4 (renaming and orientation) completed in less than a second.

@@

We have produce new and better match race schedules. These schedules can be used by anyone that
competes under the criteria published by ISAF. Our schedules can be downloaded as blank schedules
and then populated with the names of the actual competing skippers.

>>>>

\begin{abstract}
We present a constraint programming solution to the problem of generating round-robin schedules for sailing match races. Our schedules satisfy the critria published by the International Sailing Federation (ISAF) governing body for match race pairing lists. We show that some published ISAF schedules are in fact illegal, and present
corresponding legal instances and schedules that have not previously been published. Our schedules
can be downloaded as blanks, then populated with actual competitors and used in match racing competitions.
\end{abstract}

@@

The paper is organised as follows: we introduce the 13 match racing criteria, then explain the
constraint models and four stages of schedule construction, and then schedules are presented. We
finish with discussion and a conclusion.

@@

There are some conflicts inherent in the criteria. Take criteria~4 and~11, assume we have 4 boats, and
in flight $i$ the last match is the pair of skippers ($x,y$). Criterion~11 dictates that skippers $x$
and $y$ must appear in the next flight, $i+1$, and criterion~4 that neither can be first in the next
flight. This forces skippers $x$ and $y$ to compete in flight $i+1$ as the last match, violating
criterion~1. Therefore, although not explicitly stated, it is not possible to satisfy every criteria
with fewer than 6 boats.

@@

        \begin{scope}[yshift=9.9cm, xshift=-3.5cm]
            \node [anchor=north west] (ModMatchTable) at (0, 0) {
                \begin{minipage}{4.5cm}
                    \centering
                    \setlength{\tabcolsep}{2pt}
                    \setlength{\aboveep}{0pt}
                    \setlength{\belowrulesep}{0pt}
                    \setlength{\extrarowheight}{.75ex}
                    \begin{tabular}{cccccccc}
                        & 0 & 1 & 2 & 3 & 4 & 5 & 6 \\ \cmidrule{2-8}
                        \multicolumn{1}{l@{\hspace{1em}}|}{0} & ~-~ & 0 & 1 & 3 & 5 & 2 & 6 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{1} & 0 & ~-~ & 6 & 2 & 3 & 1 & 4 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{2} & 1 & 6 & ~-~ & 0 & 4 & 5 & 2 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{3} & 3 & 2 & 0 & ~-~ & 6 & 4 & 5 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{4} & 5 & 3 & 4 & 6 & ~-~ & 0 & 1 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{5} & 2 & 1 & 5 & 4 & 0 & ~-~ & 3 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{6} & 6 & 4 & 2 & 5 & 1 & 3 & ~-~ \\
                    \end{tabular}
                \end{minipage}
            };
            \node [above=-0.1 of ModMatchTable.north west, anchor=south west] (ModMatch) { $\modMatch$ };
        \end{scope}

@@

We present four pairs of schedules. The first pair is for 8 skippers and 6 boats, one published by
ISAF, the other generated by us. Next, we present two new schedules, not appearing in the ISAF
manual, for 9 skippers and 6 boats and 9 skippers with 8 boats, then 10 skippers and 6 boats, again
both published by ISAF and generated by us. Finally, we show what is a relatively easy problem, 8 skippers
and 8 boats.  For each of our schedules (with the exception of the latter ``easy-8'' problem), we used 1 day
CPU time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance.
Stages 3 and 4 (renaming and orientation) completed in less than a second.

@@

We have produced new and better match race schedules. These schedules can be used by anyone that
competes under the criteria published by ISAF. Our schedules can be downloaded as blank schedules
and then populated with the names of the actual competing skippers.
